\documentclass[a4paper]{article}
\title{JumpStart Registration System Proposal}

\begin{document}

\title{JumpStart Registration System Proposal}
\author{Team Lord of the Sprints}
\date{2017-08-27}
\maketitle

\section{Background and Motivation}
\paragraph{} JumpStart is a set of events hosted between semesters by the UTSA Library and Computer Science Department which provide supplemental instruction to freshmen CS students or transfer students on skills necessary for their oncoming course. In the past, organizers have experienced difficulty in correctly matching students to the appropriate events, due to students either already knowing the relevant material, or not knowing necessary prerequisite material.

\section{System Summary}
\paragraph{} JumpStart Registration System will contact eligible students for JumpStart event registration and direct them to a brief survey regarding their experience with relevant material. The results of the survey will be used to recommend the appropriate JumpStart events, if any, and allow the student to register for 0 or more events. The system will make registration data available to event organizers, and provide printable sign-in sheets for the day of the event. The system will contain supporting email, database, and web-server capability, as required.

\section{Major Features}
	\begin{itemize}
		\item Automatic entry of invitees as csv file.
		\item Web-based skill survey and registration.
		\item Registration access restricted to invited individuals only.
		\item Registration database.
		\item Sign-in sheet generation.
	\end{itemize}

\section{Target Platform}
\paragraph{} Server platform will be Linux. The web-page served to the user for registration \em may \em require a JavaScript-enabled browser.

\section{Competing Services}
\paragraph{} The currently implemented system has been providing some of the desired features for years, albeit with the previously described difficulties.

\paragraph{} Existing web survey services, such as Google Forms or Survey Monkey, would allow for skill surveying, but not automatic event recommendation.	

\section{Team Members}
	\begin{itemize}
		\item Garcia, Francisco\\ ftgarcia@franciscotgarcia.com
		\item Garza, Arturo\\ arturo35689@hotmail.com
		\item Garza, Oscar\\ oscar35689@hotmail.com
		\item Greenlees, Daniel\\ dgreenlees28@hotmail.com
		\item Moore, Kevin\\ Kevin.omd@gmail.com
	\end{itemize}

\end{document}